Improving the communication and accessibility of stock assessment using interactive

### 2019-05-07 analysis/paper/manuscript.Rmd
Draft an abstract

---
title: Improving the communication and accessibility of stock assessment using interactive
  visualization tools
author: "Paul M. Regular, Gregory J. Robertson, Keith P. Lewis, etc?"
date: "Fisheries and Oceans Canada, Northwest Atlantic Fisheries Center, 80 East White Hills, St. John's, Newfoundland and Labrador, A1C 5X1, Canada"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: references.bib
csl: apa.csl
---

>>>>

---
title: Improving the communication and accessibility of stock assessment using interactive
  visualization tools
author: "Paul M. Regular, Gregory J. Robertson, Keith P. Lewis, etc?"
date: "Fisheries and Oceans Canada, Northwest Atlantic Fisheries Center, 80 East White Hills, St. John's, Newfoundland and Labrador, A1C 5X1, Canada"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: references.bib
csl: apa.csl
abstract: |
  **Abstract**: In the age of data-intensive science and big data, scientists across many fields are faced with the challenge of synthesizing and communicating information from large and complex data sets. The field of stock assessment is no exception as the volume and variety of the data used in the field has grown alongside the computational methods used to integrate them. While this growth in data and model complexity has mediated some of the difficulties in assessing the status of many stocks, the process of communicating the results to stakeholders and fisheries managers in a meaningful way has become more daunting. The traditional approach of presenting information across a series of static slides often fail to convey the richness of information available and, as such, important patterns and details are easily overlooked. Here we contend that this problem can be mediated through the effective use of new open source tools for building interactive visualizations. These tools facilitate a deeper and more collective understanding of both the data and models used to inform stock assessments as they allow a broader audience to conduct detailed explorations of the results. *...need a punchy last line...*
---
